Scheeper's Meager-NWD Game and the Menger Game

### 2014-12-04 phd/dissertation/chapter2.tex
finish first draft of dissertation

\chapter{Toplogical Games and Strategies\\ of Perfect and Limited Information}

The goal of this paper is to explore the applications of limited information
strategies in existing topological games. There are a variety of frameworks
for modeling such games, so we establish one within this chapter which we
will use for this manuscript.

@@

Topological games are usually infinite games, ignoring trivial examples.
One of the earliest examples
of a topological game is the Banach-Mazur game, proposed by Stanislaw Mazur
as Problem 43 in Stefan Banach's Scottish Book (1935). A more comprehensive
history of the Banacy-Mazur and other topological games may be found in
Telgarsky's survey on the subject \cite{MR892457}.

@@

For example, if $X$ is a locally compact Hausdorff space, $\pl N$ can ``force''
a win by choosing $N_0$ such that $\cl{N_0}$ is compact, and choosing
$N_{n+1}$ such that
$N_{n+1}\subseteq\cl{N_{n+1}}\subseteq O_{n+1}\subseteq N_n$
(possible since $N_n$ is a compact Hausdorff $\Rightarrow$ normal space).
Since $\bigcap_{n<\omega} E_n = \bigcap_{n<\omega} N_n$ is the decreasing
intersection of compact sets, it cannot be empty.

>>>>

\chapter{Introduction}

The goal of this paper is to explore the applications of limited information
strategies in existing topological games.

@@

Topological games are usually infinite games, ignoring trivial examples.
One of the earliest examples
of a topological game is the Banach-Mazur game, proposed by Stanislaw Mazur
as Problem 43 in Stefan Banach's Scottish Book in 1935, and solved by
Banach later that year \cite{MR666400}. A more comprehensive
history of the Banacy-Mazur and other topological games may be found in
Telgarsky's survey on the subject \cite{MR892457}.

@@

For example, if $X$ is a locally compact Hausdorff space, $\pl N$ can ``force''
a win by choosing $N_0$ such that $\cl{N_0}$ is compact, and choosing
$N_{n+1}$ such that
$N_{n+1}\subseteq\cl{N_{n+1}}\subseteq E_{n+1}\subseteq N_n$.
Since $\bigcap_{n<\omega} E_n = \bigcap_{n<\omega} N_n$ is the decreasing
intersection of compact sets, it cannot be empty.
